\section*{Referências}

\small
ANH-HOANG, Dang; TRAN, Vu; NGUYEN, Le-Minh. \textit{Survey and analysis of hallucinations in large language models: attribution to prompting strategies or model behavior}. Frontiers in Artificial Intelligence, 2025. DOI: 10.3389/frai.2025.1622292. Disponível em: \url{https://www.frontiersin.org/articles/10.3389/frai.2025.1622292/full}. Acesso em: 8 abr. 2026.

BANDEIRA, Cristina Leston; BERNARDES, Cristiane Brum. \textit{Information vs engagement in parliamentary websites -- a case study of Brazil and the UK}. Revista de Sociologia e Política, Curitiba, v. 24, n. 59, p. 91--107, 2016. DOI: 10.5380/rsocp.v24i59.48709. Disponível em: \url{https://revistas.ufpr.br/rsp/article/view/48709}. Acesso em: 9 abr. 2026.

DEENE, Joris. \textit{Can a RAG system reduce the GDPR risks of your enterprise AI?}, 2025. Disponível em: \url{https://www.ictrechtswijzer.be/en/can-a-rag-system-reduce-the-gdpr-risks-of-your-corporate-ai/}. Acesso em: 9 abr. 2026.

GAO, Yunfan; XIONG, Yun; GAO, Xinyu; JIA, Kangxiang; PAN, Jinliu; BI, Yuxi; DAI, Yi; SUN, Jiawei; WANG, Meng; WANG, Haofen. \textit{Retrieval-augmented generation for large language models: a survey}. arXiv preprint, arXiv:2312.10997, 2023. Disponível em: \url{https://arxiv.org/abs/2312.10997}. Acesso em: 9 abr. 2026.

GAO, Yunfan; XIONG, Yun; WANG, Meng; WANG, Haofen. \textit{Modular RAG: Transforming RAG systems into LEGO-like reconfigurable frameworks}. arXiv preprint, arXiv:2407.21059, 2024. Disponível em: \url{https://arxiv.org/abs/2407.21059}. Acesso em: 9 abr. 2026.

GUPTA, Shailja; RANJAN, Rajesh; SINGH, Surya Narayan. \textit{A Comprehensive Survey of Retrieval-Augmented Generation (RAG): Evolution, Current Landscape and Future Directions}. arXiv preprint, arXiv:2410.12837, 2024. Disponível em: \url{https://arxiv.org/abs/2410.12837}. Acesso em: 8 abr. 2026.

HIGHBERG. \textit{Why the public sector can't do without explainable and responsible AI}. 2025. Disponível em: \url{https://highberg.com/insights/why-the-public-sector-cant-do-without-explainable-and-responsible-ai}. Acesso em: 8 abr. 2026.

INTER-PARLIAMENTARY UNION. \textit{Use cases for AI in parliaments}. Geneva, 2024. Disponível em: \url{https://www.ipu.org/file/20635/download}. Acesso em: 8 abr. 2026.

GEUNIS, Lotte. \textit{Parliamentary Monitoring Organizations: partners in parliamentary oversight}. International IDEA, 2023. Disponível em: \url{https://www.idea.int/publications/catalogue/html/parliamentary-monitoring-organizations-partners-parliamentary}. Acesso em: 8 abr. 2026.

KHALIQ, Mohammed Abdul; CHANG, Paul Yu-Chun; MA, Mingyang; PFLUGFELDER, Bernhard; MILETIĆ, Filip. \textit{RAGAR, Your Falsehood Radar: RAG-augmented reasoning for political fact-checking using multimodal large language models}. In: Proceedings of the Seventh Fact Extraction and VERification Workshop (FEVER), 2024, Miami, Florida, USA. Association for Computational Linguistics, 2024. p. 280--296. DOI: \url{https://doi.org/10.18653/v1/2024.fever-1.29}. Disponível em: \url{https://aclanthology.org/2024.fever-1.29/}. Acesso em: 9 abr. 2025.

KAVČIČ, Alenka; STOJANOSKI, Martin; MAROLT, Matija. \textit{Historical Parliamentary Corpora Viewer}. In: Proceedings of the IV Workshop on Creating, Analysing, and Increasing Accessibility of Parliamentary Corpora (ParlaCLARIN) @ LREC-COLING 2024, 2024, Torino. Disponível em: \url{https://aclanthology.org/2024.parlaclarin-1.19/}. Acesso em: 9 abr. 2026.

MAHARJAN, Anuj; YADAV, Umesh. \textit{Chunking, retrieval, and re-ranking: an empirical evaluation of RAG architectures for policy document question answering}. arXiv preprint, arXiv:2601.15457, 2026. Disponível em: \url{https://arxiv.org/abs/2601.15457}. Acesso em: 9 abr. 2026.

MARTELLOTE VIOLA, Carla Maria; MARQUES FELIPE, Carla Beatriz; FARIAS SALES MARQUES, Luana. \textit{Inteligência Artificial na Organização do Conhecimento do Parlamento brasileiro: um estudo aplicado aos dados e às informações legislativas}. ISKO Brasil, n. 8, 2025. Disponível em: \url{https://isko.org.br/ojs/index.php/iskobrasil/article/view/52}. Acesso em: 9 abr. 2026.

MINAEE, Shervin; MIKOLOV, Tomas; NIKZAD, Narjes; CHENAGHLU, Meysam; SOCHER, Richard; AMATRIAIN, Xavier; GAO, Jianfeng. \textit{Large Language Models: A Survey}. arXiv preprint, arXiv:2402.06196, 2024. Disponível em: \url{https://arxiv.org/abs/2402.06196}. Acesso em: 8 abr. 2026.

NIE, Zhijie; FENG, Zhangchi; LI, Mingxin; ZHANG, Cunwang; ZHANG, Yanzhao; LONG, Dingkun; ZHANG, Richong. \textit{When Text Embedding Meets Large Language Model: A Comprehensive Survey}. arXiv preprint, arXiv:2412.09165, 2024. Disponível em: \url{https://ar5iv.labs.arxiv.org/html/2412.09165}. Acesso em: 8 abr. 2026.

OPENAI. \textit{Why language models hallucinate}. 2025. Disponível em: \url{https://openai.com/index/why-language-models-hallucinate/}. Acesso em: 8 abr. 2026.

SAID, Adil. \textit{RAG in practice: exploring versioning, observability, and evaluation in production systems}. Towards AI, 28 ago. 2025. Disponível em: \url{https://towardsai.net/p/artificial-intelligence/rag-in-practice-exploring-versioning-observability-and-evaluation-in-production-systems}. Acesso em: 8 abr. 2026.

SINGH, Pankaj. \textit{8 types of chunking for RAG systems}. Analytics Vidhya, 4 abr. 2025. Disponível em: \url{https://www.analyticsvidhya.com/blog/2025/02/types-of-chunking-for-rag-systems/}. Acesso em: 8 abr. 2026.

SKUBIC, Jure; FIŠER, Darja. \textit{Parliamentary discourse research in political science: literature review}. In: Proceedings of the IV Workshop on Creating, Analysing, and Increasing Accessibility of Parliamentary Corpora (ParlaCLARIN) @ LREC-COLING, 2024. Torino, Italia. Disponível em: \url{https://aclanthology.org/2024.parlaclarin-1.1/}. Acesso em: 8 abr. 2026.

UNITED NATIONS. \textit{Responsive and accountable public governance}. New York: UN DESA, 2015. Disponível em: \url{https://desapublications.un.org/file/663/download}. Acesso em: 8 abr. 2026.

VASWANI, Ashish; SHAZEER, Noam; PARMAR, Niki; USZKOREIT, Jakob; JONES, Llion; GOMEZ, Aidan N.; KAISER, Lukasz; POLOSUKHIN, Illia. \textit{Attention is all you need}. arXiv preprint, arXiv:1706.03762, 2017. Disponível em: \url{https://arxiv.org/abs/1706.03762}. Acesso em: 8 abr. 2026.

WESTMINSTER FOUNDATION FOR DEMOCRACY. \textit{Guidelines for AI in Parliaments}. London, 2023. Disponível em: \url{https://www.agora-parl.org/sites/default/files/agora-documents/English%20-%20WFD%20AI%20Guidelines%20for%20Parliaments.pdf}. Acesso em: 8 abr. 2026.

\normalsize
